Improving Haskell Theory Exploration

### 2015-12-01 TransferReport/contributions.tex
Use simple quoted IDs

\iffalse TODO: Don't show the ``pkg:Mod:name'' format here, it will just be confusing. Leave that to the implementation section. \fi

@@

The purpose of recurrent clustering, as with other clustering algorithms, is to identify similarities between a set of inputs. In our case, we want compare the abstract syntax trees of Core expressions, which presents a difficulty for clustering: many leaves are \emph{references}, containing identifiers for other expressions. For example, consider the following expressions which are identical except for an identifier:\footnote{The \texttt{(\&\&)} function is boolean AND, \texttt{(++)} appends lists and \texttt{map} applies a function to the elements of a list.}

\begin{equation*}
  \begin{split}
    X =\ & \texttt{App}\ (\texttt{Var}\ (\texttt{Local}\ \texttt{"f"}))\ (\texttt{Var}\ (\texttt{Global}\ \texttt{"base:Prelude.(\&\&)"})) \\
    Y =\ & \texttt{App}\ (\texttt{Var}\ (\texttt{Local}\ \texttt{"f"}))\ (\texttt{Var}\ (\texttt{Global}\ \texttt{"base:Prelude.(++)"})) \\
    Z =\ & \texttt{App}\ (\texttt{Var}\ (\texttt{Local}\ \texttt{"f"}))\ (\texttt{Var}\ (\texttt{Global}\ \texttt{"base:Prelude.map"}))
  \end{split}
\end{equation*}

>>>>

@@

The purpose of recurrent clustering, as with other clustering algorithms, is to identify similarities between a set of inputs. In our case, we want compare the abstract syntax trees of Core expressions, which presents a difficulty for clustering: many leaves are \emph{references}, containing identifiers for other expressions. For example, consider the following expressions which are identical except for an identifier:

\begin{equation*}
  \begin{split}
    X =\ & \texttt{App}\ (\texttt{Var}\ (\texttt{Local}\ \texttt{"f"}))\ (\texttt{Var}\ (\texttt{Global}\ \texttt{"odd"})) \\
    Y =\ & \texttt{App}\ (\texttt{Var}\ (\texttt{Local}\ \texttt{"f"}))\ (\texttt{Var}\ (\texttt{Global}\ \texttt{"even"})) \\
    Z =\ & \texttt{App}\ (\texttt{Var}\ (\texttt{Local}\ \texttt{"f"}))\ (\texttt{Var}\ (\texttt{Global}\ \texttt{"plus"}))
  \end{split}
\end{equation*}
